\thetitle

### 2020-11-20 writing/sample.tex
reivising rational and sample for the new stats

In summary, our sampling process takes advantage of ancillary information
to deliver a  sufficiently large representative set of scenarios.
Concretely, we test each
mode of the rational programmer on 72,192 randomly selected interesting
debugging scenarios spread across both benchmarks and mutators.
Furthermore stratified random sampling allows us to derive conclusions
about the proportions of the whole population from the proportions of
our sample despite the population's heterogeneity, exactly what we need to project comparisons about the
usefulness of various modes of the
rational programmer from the sample to the set of all interesting debugging
scenarios.  Finally, we can also calculate separate estimates per stratum and provide different
viewpoints of our results. For instance, because of the size of the sample
of scenarios from the lattice of a mutant, we can estimate whether natural
blame is more useful than natural exceptions for all interesting scenarios
of each mutant with 95\% confidence and 5\% error margin.

>>>>

In summary, our sampling process takes advantage of ancillary information
to deliver a  sufficiently large representative set of scenarios.
Concretely, we test each
mode of the rational programmer on 72,192 randomly selected interesting
debugging scenarios spread across both benchmarks and mutators.
Furthermore stratified random sampling allows us to derive precise conclusions
about the proportion of the whole population that satisfies a given trait 
from the proportion of the sample 
that satisfies the trait despite the population's heterogeneity, exactly what we need to project comparisons about the
usefulness of various modes of the
rational programmer from the sample to the set of all interesting debugging
scenarios.  Finally, we can also calculate separate estimates per stratum
and provide an alternative
viewpoint of our results. For instance, because of the size of the sample
of scenarios from the lattice of a mutant, we can estimate whether natural
blame is more useful than natural exceptions for all interesting scenarios
of each mutant with 95\% confidence and 5\% error margin.
